### 2024-06-08 journal/preliminaries.tex
fixed defn of wait-free

We use the standard correctness requirement of linearizability \cite{HW90} for 
our queue.  This means that for every execution of our queue implementation,
there should be a sequential ordering (called the linearization) of 
a subset of the operations, including all completed operations,
satisfying two properties.  First, if one operation terminates before another
begins, they must appear in the same order in the linearization.
Second, each completed operation must return the same response that it would
if the operations were done sequentially in their linearization order.
(In fact, our implementation also satisfies the stronger requirement of being
strongly linearizable \cite{GHW11}.)
The termination condition that our queue satisfies is wait-freedom:
no operation by a process can take infinitely many steps of the process to complete.

>>>>

We use the standard correctness requirement of linearizability \cite{HW90} for 
our queue.  This means that for every execution of our queue implementation,
there should be a sequential ordering (called the linearization) of 
a subset of the operations, including all completed operations,
satisfying two properties.  First, if one operation terminates before another
begins, they must appear in the same order in the linearization.
Second, each completed operation must return the same response that it would
if the operations were done sequentially in their linearization order.
(In fact, our implementation also satisfies the stronger requirement of being
strongly linearizable \cite{GHW11}.)
The termination condition that our queue satisfies is wait-freedom:
each operation by a process is guaranteed to terminate within a finite number of the process's own steps.
